---
editor_options: 
  markdown: 
    wrap: sentence
---

------------------------------------------------------------------------

title: "lab-04.md" output: word_document date: "2026-03-18"

# Lab-04

## Selection Bias and Measurement Bias

In today's lesson week 4 we learnt about the selection use of fork, chain, and collider structures to recognise how bias enters a study including the classification of four structural types of error.
We also learnt how to condition of selection bias affects causal contrasts.
Relevent diagrams were discussed.
In the lab we learnt followings:

\* How to write a simple regression formula in R.

\* How adding a second predictor can change a coefficient.

\* How an interaction changes fitted lines.

\* How to rerun a model after changing the formula.

The lessons were interesting but challenging.
Need to revise by further studies.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
